\input{../preamble}

\author{Serena Spinoso}

\begin{document}

\section{VERIGRAPH}
VeriGraph is a verification tool based on the state of the art SMT solver, Z3. This tool aims at performing the VNF graph verification, through an intensive modelling activity. VeriGraph includes models of both the whole network and forwarding behaviours of each involved VNF. Those models are expressed by means of first-order logic formulas and allow to verify if reachability properties hold in the network (i.e., source node can reach a destination node passing through a set of network functions). In order to exhaustively verify all the possible service chains available in a given VNF graph, VeriGraph exploits an external tool, namely Neo4JManager, to extract all the paths from the source node to the destination node. Then, VeriGraph is able to generate a model for each extracted chain. Using the VNF chain model, the verification tool can perform a complete verification step. In detail, VeriGraph (and, in turn, Z3) looks for some assignment of appropriate values to uninterpreted functions and constant symbols that compose the VNF chain formulas, in order to make the chain formulas satisfiable. Here we present how network and VNFs in the catalog are modelled in VeriGraph, that is the set of the main formulas that represent the behaviours of both network and VNFs. 

\subsection{NETWORK MODEL}
\input{network_model}  

\subsection{VNF MODEL}
\label{VNFmodels}
\input{vnf_model}

%\subsection{AUTOMATIC CREATION OF REACHABILITY TESTS}
%\label{algorithm}
%\input{algorithm.tex}
%
%\subsubsection{VNF chains format example}
%\label{chains}
%\input{chain_list_format}

\subsubsection{VNF configurations}
\label{configuration}
\input{VNF_configuration}

\end{document}